Label object representation and manipulation with ITK

### 2007-10-01 article/Article.tex
a few words about the LabelMapOvelayImageFilter and LabelMapToRGBImageFilter classes
darcs-hash:20071001085036-2fc9d-ea7bdff0c10daa257cee41b0f0787ac3066c87d0.gz

\begin{figure}[htbp]
\begin{center}
\subfigure[A label image]{\includegraphics[scale=.7]{cthead1-label2-rgb}}
\subfigure[All the objects smaller than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-bigger-than-1000}}
\subfigure[All the objects greater than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-smaller-than-1000}}
\subfigure[All the objects with roundness smaller than 0.8 removed]{\includegraphics[scale=.7]{cthead1-label2-roundness-greater-than-0_8}}
\subfigure[All the objects with elongation smaller than 10 removed]{\includegraphics[scale=.7]{cthead1-label2-binaryElongation-greater-than-10}}
\subfigure[All the objects with perimeter smaller than 100 removed]{\includegraphics[scale=.7]{cthead1-label2-perimeter-greater-than-100}}
\caption{Some example of opening with different attribute and parameters.}
\end{center}
\end{figure}

@@

Once the manipulation of the objects is done, it can be useful to go back to a
more classic {\em itk::Image}. Several classes are provided to do that:
\begin{itemize}
  \item The {\em itk::LabelMapToLabelImageFilter} class simply
convert a {\em itk::LabelMap} to a label image stored in a {\em
itk::Image}.
  \item The {\em itk::LabelMapToBinaryImageFilter} put all the
objects in the foreground of a binary image stored in a {itk::Image}. It is
intended to be used with an image produced by the {\em
itk::BinaryImageToLabelMapFilter}. The background values of the
original image can also be restored by this filter.
  \item The {\em itk::LabelMapMaskImageFilter} class can be used
to mask an image with the objects of the {\em itk::LabelMap}. With
that filter, the image can be cropped to contain only the non-masked zone\footnote{
The code used to produce the output region based on the content of the image
is partially copied from a contribution of Peter Cech \url{http://www.vision.ee.ethz.ch/~pcech/itkAutoCropImageFilter/}.}
, or the non-masked zone padded by a user defined number of pixels.
  \item Finally, {\em itk::LabelMapToAttributeImageFilter} produce
an {\em itk::Image} with the value of the attribute of the objects of the {\em
itk::LabelMap}. This filter is mostly useful to have a global view
of the attribute values in the image.
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{nuclei-overlay}
\caption{The segmented nuclei. The too small objects and the ones on the border have been excluded.}
\label{fig:overseg}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[A label image]{\includegraphics[scale=.7]{cthead1-label2-rgb}}
\subfigure[All the objects smaller than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-bigger-than-1000}}
\subfigure[All the objects greater than 1000 pixels removed]{\includegraphics[scale=.7]{cthead1-label2-size-smaller-than-1000}}
\subfigure[All the objects with roundness smaller than 0.8 removed]{\includegraphics[scale=.7]{cthead1-label2-roundness-greater-than-0_8}}
\subfigure[All the objects with elongation smaller than 10 removed]{\includegraphics[scale=.7]{cthead1-label2-binaryElongation-greater-than-10}}
\subfigure[All the objects with perimeter smaller than 100 removed]{\includegraphics[scale=.7]{cthead1-label2-perimeter-greater-than-100}}
\caption{Some example of opening with different attribute and parameters.
Note that the labels are kept unchanged in the output image.}
\end{center}
\end{figure}

@@

Once the manipulation of the objects is done, it can be useful to go back to a
more classic {\em itk::Image}. Several classes are provided to do that:
\begin{itemize}
  \item The {\em itk::LabelMapToLabelImageFilter} class simply
convert a {\em itk::LabelMap} to a label image stored in a {\em
itk::Image}.
  \item The {\em itk::LabelMapToBinaryImageFilter} put all the
objects in the foreground of a binary image stored in a {itk::Image}. It is
intended to be used with an image produced by the {\em
itk::BinaryImageToLabelMapFilter}. The background values of the
original image can also be restored by this filter.
  \item The {\em itk::LabelMapMaskImageFilter} class can be used
to mask an image with the objects of the {\em itk::LabelMap}. With
that filter, the image can be cropped to contain only the non-masked zone\footnote{
The code used to produce the output region based on the content of the image
is partially copied from a contribution of Peter Cech \url{http://www.vision.ee.ethz.ch/~pcech/itkAutoCropImageFilter/}.}
, or the non-masked zone padded by a user defined number of pixels.
  \item The {\em itk::LabelMapToAttributeImageFilter} produce
an {\em itk::Image} with the value of the attribute of the objects of the {\em
itk::LabelMap}. This filter is mostly useful to have a global view
of the attribute values in the image.
  \item The {\em LabelMapToRGBImageFilter} produce a color {\em itk::Image} with
{\em itk::RGBPixel} as pixel type. The label objects are in color, as in
Figure~\ref{fig:labelImage}. This class is mostly useful for a quick visual
validation without going outside ITK.
  \item Finally, the {\em LabelMapOvelayImageFilter} produce a color {\em itk::Image} with
{\em itk::RGBPixel} as pixel type. The label objects are in color on top of a grayscale
image, as in Figure~\ref{fig:nucleiOverlay}. This class is mostly useful for a quick visual
validation without going outside ITK.
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{nuclei-overlay}
\caption{The segmented nuclei. The too small objects and the ones on the border have been excluded.}
\label{fig:nucleiOverlay}
\end{center}
\end{figure}
